\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 lang-design.tex
resolve comments and add new comments

When adapting Family Polymorphism into dependent types, we choose to
focus only on the essence of family (and inheritance)
structure in \citet{zm2017}, and thus a lot of unrelated features, like
Interface, will be removed. In this case, it will look like module with
late-binding. Inheritance can be considered as code and proof reuse mechanism for module. We also
need it to have good compatibility with inductive types, because we
don't want to diverge too much from the routine Coq programming experience\YZ{By 'reasoning power of Coq', I suppose you mean the expressive power of Gallina?}\EDJreply{I think the sentence last time was not really making sense because using Church Encoding of inductive doesn't sabotage the expressiveness. I rephrase it now, please check.}
(and its tactic programming).

@@

We use "Family" and "EndFamily" to scope, and "Field" is used to declare new field members in family.\YZ{This sentence sounds a bit recursive}\EDJreply{What about now?}
We can define nested families.
Family will also be used to encode recursive handlers. Each case
handling of one inductive type will be aggregated into one family, then
"FRecursor" will be used to construct a recursor using these handlers.
For example, \mintinline{Coq}{FRecursor recur about T motive f} "using"
"handlers" will generate a new field "recur" that is doing induction
(using elimination principle of "T") using motive "f", and the handlers
are located in the family "handlers".

>>>>

When adapting Family Polymorphism into dependent types, we choose to
focus only on the essence of family (and inheritance)
structure in \citet{zm2017}, and thus a lot of unrelated features, like
Interface, will be removed. In this case, it will look like module with
late-binding. Inheritance can be considered as code and proof reuse mechanism for module. We also
need it to have good compatibility with inductive types, because we
don't want to retain the idiomatic Coq programming experience
%\YZ{By 'reasoning power of Coq', I suppose you mean the expressive power of Gallina?}\EDJreply{I think the sentence last time was not really making sense because using Church Encoding of inductive doesn't sabotage the expressiveness. I rephrase it now, please check.}
(and its tactic programming).

@@

We use "Family" and "EndFamily" to scope, and "Field" is used to declare new members in a family.
We can define nested families.
Family will also be used to encode recursive handlers. Each case
handling of one inductive type will be aggregated into one family, then
"FRecursor" will be used to construct a recursor using these handlers.
For example, \mintinline{Coq}{FRecursor recur about T motive f} "using"
"handlers" will generate a new field "recur" that is doing induction
(using elimination principle of "T") using motive "f", and the handlers
are located in the family "handlers".
